---
title: "How to use crrri?"
subtitle: "Some introductive examples"
author: "Christophe Dervieux"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use crrri?}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = TRUE,
  comment = "#>"
)
Sys.unsetenv("DEBUGME")
```

The `crrri` package provides a _Chrome Remote Interface_ for R. It is inspired by the node.js module [`chrome-remote-interface`](https://www.npmjs.com/package/chrome-remote-interface).

This vignette aims to show several examples of usage for `crrri`.

All the examples come from the [`chrome-remote-interface`](https://www.npmjs.com/package/chrome-remote-interface) or [`puppeteer`](https://www.npmjs.com/package/puppeteer) documentations. This vignette shows how to reproduce those using `crrri`.

# Setup

You have to set up beforehand the `HEADLESS_CHROME` environment variable to a Chromium/Chrome binary on our system. If you do not, you will need to provide the path to a Chromium/Chrome binary in `chr_connect`.  
The [`pagedown`](https://cran.r-project.org/package=pagedown) package provides a helper function to retrieve the Chromium/Chrome path on your system: `pagedown::find_chrome()`. So, you can first execute:

```{r, eval=FALSE}
Sys.setenv(HEADLESS_CHROME = pagedown::find_chrome())
```

We need to load `crrri` and also `promises` to have the tools to deals with
_promises_ that `crrri` is based on.

```{r}
library(crrri)
library(promises)
```

# Example 1: Take a screenshot

This first example is inspired from this
[post](https://jonathanmh.com/taking-full-page-screenshots-headless-chrome/) that uses the `chrome-remote-interface` node.js package.

```{r chrome-screenshot, results='hide'}
targetUrl <- "https://cran.rstudio.com"
viewport <- c(1440, 900)
screenshotDelay <- 2 # seconds
screenshot_file <- tempfile(fileext = ".png")

chrome_con <- chr_connect()

screenshot <- 
  chrome_con %>%
  # enable events for the Page, Dom and Network domains 
  Page.enable() %>%
  DOM.enable() %>%
  Network.enable() %>%
  Emulation.setDeviceMetricsOverride(
    width = viewport[1],
    height = viewport[2],
    deviceScaleFactor = 0,
    mobile = FALSE,
    dontSetVisibleSize = FALSE
  ) %>%
  # go to url
  Page.navigate(targetUrl) %>%
  Page.loadEventFired() %>%
  # add a delay 
  wait(delay = screenshotDelay) %>%
  # capture screenshot
  Page.captureScreenshot(format = "png", fromSurface = TRUE) %...>% 
  {
    .$result$data %>% jsonlite::base64_dec() %>% writeBin(screenshot_file)
  } %>%
  # close the chrome connexion
  finally(~ chr_disconnect(chrome_con)) %...!% {
    cat("Global error\n", .$message)
  }
```

```{r, include=FALSE}
# since screenshot is an invisible promise, we have to force await 
await(screenshot)
```

The screenshot is written to disk and looks like this:
```{r, echo=FALSE}
img <- magick::image_read(screenshot_file)
magick::image_scale(img, "400")
```

# Example 2: Dump HTML after page loaded

This example is inspired from this [JS script](https://github.com/cyrus-and/chrome-remote-interface/wiki/Dump-HTML-after-page-load) from the `chrome-remote-interface` wiki that dump the DOM.

```{r dump-dom, results='hide'}
chrome_con <- chr_connect()
html_file <- tempfile(fileext = ".html")

dump_dom <- 
  chrome_con %>%
  Network.enable() %>%
  Page.enable() %>%
  Network.setCacheDisabled(cacheDisabled = TRUE) %>%
  Page.navigate(url = "https://github.com", awaitResult = FALSE) %>% # because the following event listener does not use this result, it is safer to use awaitResult = FALSE
  Page.loadEventFired() %>%
  Runtime.evaluate(expression = 'document.documentElement.outerHTML') %...>% {
   writeLines(c(.$result$result$value, "\n"), con = html_file) 
  } %>%
  # Close the connexion when finish
  finally(~ chr_disconnect(chrome_con)) %...!% {
    cat(.$message)
  }
```

```{r, include=FALSE}
# since dump_dom is an invisible promise, we have to force await 
await(dump_dom)
```

Here is the first 20 lines of what we get in `html_file`:

```{r, echo = FALSE, results='asis'}
cat(paste0(
  c("```html", readLines(html_file, n = 20), "```"), 
  collapse = "\n"
))
```

This could be useful to parse HTML with `rvest` after a page is loaded. 
